---
title: "The Quarto (silly) example"
author: "Jürgen Wilbert"
date: "11. October 2022"
table-of-contents: true
---

# header one

## header two

### header three

This is *italic* this is **bold**, and ***this is both!***.

An unordered list:

-   Helmut
-   Gerhard
-   Angela

An ordered list:

1.  Bush
2.  Obama
3.  Trump

Combined:

1.  Sour
    -   Lime
    -   Envy
2.  Sweet
    -   Honey
    -   Love

# Example

Now follow some examples. We start with some analyses on Star Wars characters.

The package `dplyr` has a database included.

## Starwars

```{r}
#| include: false
library(dplyr) # needed for the starwars database
library(knitr) # needed for the kable() function
```

The Starwars data-set contains the following variables: `r names(starwars)`.

### Question 1: Do different species have different heights?

```{r}
#| echo: false
#| fig-cap: "Height distribution of Star Wars species"
#| label: fig-height

dat <- starwars[starwars$species %in% c("Droid", "Human", "Wookiee"),]
boxplot(dat$height ~ dat$species)
```

Yes, as we can see from @fig-height, not all species have the same height distribution.

### Question 2: Is there a gender bias in Star Wars?

```{r}
#| label: tbl-gender
#| tbl-cap: Gender distribution of Star Wars characters
tab <- table(starwars$gender)
kable(tab)
```

Take a look at @tbl-gender. There is a clear bias towards male characters.

### Question 3: From which homeworlds do the characters come from?

@tbl-homeworld shows which species are located at which homeworld.

```{r}
#| label: tbl-homeworld
#| tbl-cap: Homeworlds by species
#| code-fold: true
filter <- names(which(table(starwars$species) > 2))
dat <- starwars[starwars$species %in% filter,]
tab <- table(dat$homeworld, dat$species)
tab <- rbind(tab, total = margin.table(tab, 2))
tab <- cbind(tab, total = margin.table(tab, 1))

kable(tab)
```
